\HeaderA{dbeCalcSim}{CI and CV calculation}{dbeCalcSim}
\keyword{methods}{dbeCalcSim}
\begin{Description}\relax
Method for calculating coefficients of variation or confidence intervals from dbeOutputSim object estimates. This function is equivalent
to \code{dbeCalc} for dbeOutput but with the \code{update} argument always set equal to TRUE
\end{Description}
\begin{Usage}
\begin{verbatim}
dbeCalcSim(object,type="CI",vrbl="l",probs=c(0.025,0.975),replicates=FALSE,...)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{object}] A \code{dbeOutputSim} object.
\item[\code{type}] Character. "CI" for confidence interval calculation, or "CV" for coefficients of variation.
\item[\code{vrbl}] Character specifying 'dbeOutput' estimates on which calculation is applied : "l" for length structure, "a" for age structure, "n" for total number estimates, "w" for total weight estimates.
\item[\code{probs}] Numeric vector of probabilities with values in [0,1]. Defines CI bounds (relevant only if \code{type="CI"}). See \code{quantile}.
\item[\code{replicates}] Logical. If \code{TRUE}, calculation is made from @...\$rep elements ; if \code{FALSE}, @...\$estim and @...Var 'dbeOutput' data are used.
\item[\code{...}] Further arguments used as '\code{quantile} method input parameter (if \code{type="CI"} and besides \code{probs} parameter).
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
If calculation is made from replicates (see \emph{replicates} parameter), confidence interval is estimated using \emph{quantile} function with \emph{probs} and \dots parameters.
If calculation is made from estimates, normal distribution of total estimates is assumed to compute confidence intervals. 
Possible resulting negative bounds are automatically replaced by 0 in output object.
\end{Details}
\begin{Author}\relax
Dorleta Garcia \email{dgarcia@azti.es}
\end{Author}
\begin{SeeAlso}\relax
\code{\LinkA{dbeOutputSim}{dbeOutputSim}}, \code{\LinkA{dbeCalc}{dbeCalc}} \code{\LinkA{quantile}{quantile}}
\end{SeeAlso}

